SVG: The Paper

### 2022-06-10 Analysis/index.Rmd
working on some timing stuff

>>>>

drt <- filter(d, found == 40)

```{r}
# try doing per trial
a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60)  ->timedat

timedat %>%
  ggplot(aes(time_taken, acc, colour = condition)) + 
  geom_jitter(alpha = 0.2, height = 0.005, width = 0) +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)

library(brms)

my_model <- brm(acc ~ time_taken:condition + (1|observer), timedat)

a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  arrange(observer, condition, trial, found) %>%
  mutate(
    RTd = log(RT - lag(RT)),
    RTd = if_else(found == 1, 0, RTd)) %>%
  filter(RTd < 2, is.finite(RTd)) %>%
  mutate(
    time_bin = cut(RTd,breaks = 50, labels = FALSE)) %>%
  group_by(observer, condition, time_bin) %>%
  summarise(acc = mean(selected_max)) %>%
  ggplot(aes(time_bin, acc, group = observer)) +
  geom_path(alpha = 0.2) +
  geom_smooth(se= F, alpha = 0.1, method = lm) + 
  facet_grid(found~condition)
